Where is the Context for Disambiguation? An Experimental Analysis.

### 2013-11-26 draft.tex
Adding table results. Adding datasets description.

@@

\subsection{Paragraph-based context}

>>>>

%Carol Begin

\textbf{Infobox} dataset stands as a complete coverage of all Wikipedia properties, which represents all properties from all infoboxes and templates within all articles from Wikipedia. It uses the http://dbpedia.org/property/  namespace  to represent extracted information, which directly reflect the name of the Wikipedia infobox property. For the 3.8 version, there are approximately 8000 different property types.

\textbf{Mapping-based properties}, in turn, it is a hand-generated mappings of Wikipedia infoboxes/templates. The major difference between Mapping-based and Infobox datasets relies in the fact that the Mapping-based is much cleaner and better structured than Infobox. However,  due to this extraction method, Mapping based  doesn't cover all infobox types and infobox properties within Wikipedia as Infobox does.

\textbf{Instance types}, also known as Mapping-based Types, like the Mapping-based properties dataset, is a hand-generated mappings of Wikipedia infoboxes/templates, which extracts the types instead of properties. It is a DBpedia Ontology RDF type statements, that are extracted from infoboxes.

\textbf{Wikilinks} dataset contains all intern links between DBpedia resources, which is the result of the extraction of all internal links between Wikipedia articles.

In order to extract individual context from the DBpedia datasets listed above, each dataset was grouped by subject (uri), and all resources related to each uri mapped into their respective labels from the Labels dataset - which represents the titles of all Wikipedia Articles, tokenized and then counted. As a complement to the object context,  properties extraction was also covered for both Mapping-Based Properties and Infobox, as such datasets offer information at both levels - object and property.

%Carol End

@@

%Carol Begin

\begin{table}[ht] 
\caption{Objects Context Accuracy}
\centering
\begin{tabular}{c c c c}
\hline\hline 
Ontology Dataset	& Milne 	& CSAW 	& CoNLL \\ [0.5ex] 
\hline 
Infobox 			& 0.607	& 0.575	& 0.623 \\ 
MappingBased 		& 0.576 	& 0.508 	& 0.549 \\ 
Pagelinks 			&  		&  		& 0.311 \\ 
InstanceTypes 		& 0.583	& 0.520	& 0.514 \\  [1ex] 
\hline
\end{tabular} 
\label{table:nonlin} 
\end{table}

\begin{table}[ht] 
\caption{Properties Context Accuracy} 
\centering
\begin{tabular}{c c c c}
\hline\hline 
Ontology Dataset	& Milne 	& CSAW 	& CoNLL \\ [0.5ex] 
\hline 
Infobox 			& 0.617	& 0.562	& 0.567 \\ 
MappingBased 		& 0.611 	& 0.500 	& 0.514 \\ 
Pagelinks 			&  -		&  -		& - \\ 
InstanceTypes 		&  -		&  -		& - \\  [1ex] 
\hline
\end{tabular} 
\label{table:nonlin} 
\end{table}

\begin{table}[ht] 
\caption{Objects and Properties Context Accuracy} 
\centering
\begin{tabular}{c c c c}
\hline\hline 
Ontology Dataset	& Milne 	& CSAW 	& CoNLL \\ [0.5ex] 
\hline 
Infobox 			& 0.590	& 0.582	& 0.633 \\ 
MappingBased 		& 0.604 	& 0.507 	& 0.551\\ 
Pagelinks 			&  -		&  -		&  -\\ 
InstanceTypes 		&  -		&  -		& - \\ [1ex] 
\hline
\end{tabular} 
\label{table:nonlin} 
\end{table}

\begin{table}[ht] 
\caption{POS Accuracy}
\centering
\begin{tabular}{c c c c}
\hline\hline 
Ontology Dataset		& Milne 	& CSAW 	& CoNLL \\ [0.5ex] 
\hline 
left tokens 			& 		&	 	&  \\ 
right tokens			&  		&  		&  \\ 
right and left tokens		& 		& 		&  \\  [1ex] 
\hline
\end{tabular} 
\label{table:nonlin} 
\end{table}

%Carol End
